---
title: "IAM-Poisson-Regression-Predictor"
author: "Nick V. Flor"
date: "2023-01-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lmtest)
```

# READ DATASET
################################################################################
```{r}
#df=read.csv("predict-count-Lexicon-Nursing-Transcript.csv")
#df=read.csv("predict-count-Lexicon-Culture-1-Transcript.csv")
#df=read.csv("predict-count-Lexicon-Culture-2-Transcript.csv")
df=read.csv("predict-count-Lexicon-ALL-Transcript.csv")
summary(df)
```


# PERFORM LINEAR REGRESSION: PHASE 1
################################################################################
```{r}
#
# Model 1
#
model1=lm(apI~cpI+cpII+cpIII+cpIV+cpV  , data = df)
plot(model1, 1:5)
summary(model1)
```


# PERFORM LINEAR REGRESSION: PHASE 2
################################################################################
```{r}
#
# Model 2
#
model2=lm(apII~cpI+cpII+cpIII+cpIV+cpV , data = df)
plot(model2, 1:5)
summary(model2)
```


# PERFORM LINEAR REGRESSION: PHASE 3
################################################################################

``` {r}
#
# Model 3
#
model3=lm(apIII~cpI+cpII+cpIII+cpIV+cpV, data = df)
plot(model3, 1:5)
summary(model3)
```


# PERFORM LINEAR REGRESSION: PHASE 4
################################################################################
```{r}
#
# Model 4
#
model4=lm(apIV~cpI+cpII+cpIII+cpIV+cpV , data = df)
plot(model4, 1:5)
summary(model4)
```


# PERFORM LINEAR REGRESSION: PHASE 5
################################################################################
```{r}
#
# Model 5
#
model5=lm(apV~cpI+cpII+cpIII+cpIV+cpV  , data = df)
plot(model5, 1:5)
summary(model5)
```


# Regression Assumption Tests
################################################################################
```{r}

# Independence assumption: residuals independent
independenceAssumption1 = lmtest::dwtest(model1) # FAIL
independenceAssumption2 = lmtest::dwtest(model2) # PASS
independenceAssumption3 = lmtest::dwtest(model3) # FAIL
independenceAssumption4 = lmtest::dwtest(model4) # PASS
independenceAssumption5 = lmtest::dwtest(model5) # PASS

# Homoscedasticity assumption:  constant error variance across predictors
homoAssumption1 = lmtest::bptest(model1) # FAIL
homoAssumption2 = lmtest::bptest(model2) # FAIL
homoAssumption3 = lmtest::bptest(model3) # FAIL
homoAssumption4 = lmtest::bptest(model4) # FAIL
homoAssumption5 = lmtest::bptest(model5) # FAIL

# Normality assumption: errors are normally distributed
normAssumption1 = shapiro.test(model1$residuals) # FAIL
normAssumption2 = shapiro.test(model2$residuals) # FAIL
normAssumption3 = shapiro.test(model3$residuals) # FAIL
normAssumption4 = shapiro.test(model4$residuals) # FAIL
normAssumption5 = shapiro.test(model5$residuals) # FIAL

```
#
#
# POISSON REGRESSION RESULTS
#
#


# PERFORM POISSON REGRESSION: PHASE 1
################################################################################
```{r}
#
# Model 1
#
model1r=glm(apI~cpI+cpII+cpIII+cpIV+cpV  , family = "poisson", data = df)
hist(df$apI)
hist(residuals(model1r))
summary(model1r)
```

# PERFORM POISSON REGRESSION: PHASE 2
################################################################################
```{r}
#
# Model 2
#
model2r=glm(apII~cpI+cpII+cpIII+cpIV+cpV , family = "poisson", data = df)
hist(df$apII)
hist(residuals(model2r))
summary(model2r)
```


# PERFORM POISSON REGRESSION: PHASE 3
################################################################################
```{r}
#
# Model 3
#
model3r=glm(apIII~cpI+cpII+cpIII+cpIV+cpV, family = "poisson", data = df)
hist(df$apIII)
hist(residuals(model3r))
summary(model3r)
```


# PERFORM POISSON REGRESSION: PHASE 4
################################################################################
```{r}
#
# Model 4
#
model4r=glm(apIV~cpI+cpII+cpIII+cpIV+cpV , family = "poisson", data = df)
hist(df$apIV)
hist(residuals(model4r))
summary(model4r)
```


# PERFORM POISSON REGRESSION: PHASE 5
################################################################################
```{r}
#
# Model 5
#
model5r=glm(apV~cpI+cpII+cpIII+cpIV+cpV  , family = "poisson", data = df)
hist(df$apV)
hist(residuals(model5r))
summary(model5r)
```


# Poisson Regression Assumption Tests
# 1. Response variable is a Poisson distribution.
# 2, Response mean = predicted value
# 3. Response variance = mean
# 4. Residuals independent
################################################################################
```{r}
# TODO
```

